---
title: "R Notebook"
output: html_notebook
---

```{r}
library()
```

library() a new tab which shows the R packages that are available because they have been installed.

```{r}
search()
```
search() shows which packages are currently loaded.

```{r}
# to get help on using install.packages
?install.packages

# Note: the parameter is a quoted string!
install.packages("seqinr",repos="https://cran.rstudio.com/")   
```
?install packages is used to get help documentation for the function. The information appears on the Help tag on the bottom right corner of the screen.

install.packages installs the package and the progress is shown in the console.
```{r}
library(help="seqinr")
```
library(help="seqinr") opens a new tab which contains the documentation for the package seqinr.

```{r}
library(seqinr)
ls("package:seqinr")
```
This loads the package and lists the functions available in the package.

```{r}
?seqinr::a 
```
?seqinr::a will open the Help tab and shows the documentation on the function a in the seqinr package.

```{r}
seqinr::a("Tyr")
```
```{r}
seqinr::words(3, c("A", "G", "C", "U"))
```
This function produces all the possible 3-letter words that can be made from the letters "A", "G", "C", and "U".
```{r}
?data
```
The documentation for the function data from the utils package is shown in the Help tab.
```{r}
data(package="seqinr")            # list the available data
```
The data sets in the package are shown in a different tab.
```{r}
data(aaindex, package="seqinr")   
```
This command loads the aaindex data set into the environment. It can now be used.
```{r}
aaindex$FASG890101 
```
```{r}
aaindex$PONJ960101 
```

Information about the amino acids at the two indices indicated are produced.

```{r}
plot(aaindex$FASG890101$I,
     aaindex$PONJ960101$I,
     xlab="hydrophobicity", ylab="volume", type="n")
text(aaindex$FASG890101$I,
     aaindex$PONJ960101$I,
     labels=a(names(aaindex$FASG890101$I)))
```
The single-letter codes of the amino acids are plotted based on their hydrophobicity (x-axis) and volume (y-axis).
```{r}
seqinr::choosebank("swissprot")
mySeq <- seqinr::query("mySeq", "N=MBP1_YEAST")
mbp1 <- seqinr::getSequence(mySeq)
seqinr::closebank()
x <- seqinr::AAstat(mbp1[[1]])
barplot(sort(x$Compo), cex.names = 0.6)
```

```{r}
library(seqinr)
choosebank("swissprot")
mySeq <- query("mySeq", "N=MBP1_YEAST")
mbp1 <- getSequence(mySeq)
closebank()
x <- AAstat(mbp1[[1]])
barplot(sort(x$Compo), cex.names = 0.6)
```
Another way to plot, but without explicitly stating which package the functions come from.
```{r}
if (! requireNamespace("seqinr", quietly=TRUE)) {
  install.packages("seqinr")
}
```
This ensures that the package is only installed when it has not been install before, instead of installing it every time.




